Canonical rings of log spin stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
edits to remarks on congruence subgroups

\begin{example}
\label{eg:congruence-bounds}
Suppose $\Gamma \subset SL_2(\BZ)$ is any congruence subgroup. Then, since
the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer order 1, 2 and 3, and has a cusp, the 
action of $\Gamma$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.
Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
generated in degree at most $5$ with relations in degree at most $10$. In fact, it is not difficult to reduce generation in weight at most 5 to generation in weight at most 4, as noted in Remark ~\ref{rem:cusp-generation-4}. Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because there is a cusp, so $\delta > 0$.
\end{example}

@@

\begin{rem}
\label{rem:cusp-generation-4}
Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}. A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in degree at most 4. This is $\delta > 0$, so $L_X$ is effective. Addtionally, $R_{L_X}$ is generated in degree 1, and inductively applying Lemma ~\ref{lem:sat-1} only adds generators in degree 3 and 4. Therefore, $R_L$ is generated in degree at most 4. Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in degree at most 4.
\end{rem}

>>>>

\begin{example}
\label{eg:congruence-bounds}
Suppose $\Gamma \subset SL_2(\BZ)$ is any congruence subgroup. Then, since
the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer order 1, 2 and 3, and has a cusp, the 
action of $\Gamma$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.
Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
generated in degree at most $5$ with relations in degree at most $10$. In fact, it is not difficult to reduce generation in weight at most 5 to generation in weight at most 4 with relations in weight at most 8, as noted in Remark ~\ref{rem:cusp-generation-4}. Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because there is a cusp, so $\delta > 0$.
\end{example}

@@

\begin{rem}
\label{rem:cusp-generation-4}
Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}. A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in weight at most 4. Since $\delta > 0$, $L_X$ is effective. Addtionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8. Therefore, $R_L$ is generated in weight at most 4 with relations in weight at most 8. Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in weight at most 4 with relations in weight at most 8.
\end{rem}
